Non-standard evaluation inside functions and loops

### 2023-04-04 text/23/non-standard-evaluation.Rmd
Minor touch-up of non-standard-evaluation

You always have the option of using the power and simplicity dplyr for most of your code and only falling back on earlier code when you need to do something inside a loop or function.

As for me, I plan to "embrace" the complexities associated with NSE. I like dplyr, ggplot2, and so many other of the tidyverse packages so much that I will find a way to remember things like `.data`, the `...` argument, and the `any_of / all_of` functions

>>>>

You always have the option of using the power and simplicity of dplyr for most of your code and only falling back on earlier code when you need to do something inside a loop or function.

As for me, I like dplyr, ggplot2, and so many other of the tidyverse packages so much that I will plan to "embrace" coding hacks like `.data`, the `...` argument, and the `any_of / all_of` functions
